---
title: "STATS 405 - HW2"
author: "Yuan Yi Chen (Eve)"
date: "2017年5月30日"
output: html_document
---

###Notes
1. I have done all the questions except the question 2 - Set primary key
2. I use "RSQLite" package instead of "RMySQL" because I cannot load this package

***
###A. Set up the Working Environment
Remove Objects
```{r, message=FALSE}
rm(list=ls())
```


Clear Memory
```{r, message = FALSE}
gc(reset=TRUE)
```

Set root
```{r, message = F}
setwd("C:/Users/Eve/Dropbox/UCLA Files/Courses/405 Data Management/HW2")
```

Package Install
```{r, message = F}
library(dplyr)
library(data.table)		#Data management package
library(DBI)  
```


***

###B. Connect database and add data sets into the database (two data sets - Breast cancer diagnostic & prognostic)
```{r, message = F}
library(RSQLite)
SQLite()
```

```{r, message = F}
con <- dbConnect(SQLite(), db = "database.sqlite")  #dbconnect
```

Remove data sets from our database
```{r, message = F}
dbRemoveTable(con, "Diag")
dbRemoveTable(con, "Prog")
```

Add our data sets to our database
```{r, message = F}
#Load data set - Breast cancer diagnostic data set
dbWriteTable(conn = con, name = "Diag", value = "diag.csv",
             row.names = F, header = T)

#Load data set - Breast cancer prognostic data set
dbWriteTable(conn = con, name = "Prog", value = "prog.csv",
             row.names = F, header = T)
```

List all the data sets and colnames
```{r, message = F}
dbListTables(con)
dbListFields(con, "Diag")  #See colnames of Diag (diagnostic data set)
dbListFields(con, "Prog")  #See colnames of Piag (prognostic data set)
```

Take a look about these data sets
```{r}
#(a.) Diag data set
dbGetQuery(con, "SELECT * FROM Diag
                   WHERE ID_number = '842517'")

#(b.) Prog data set
dbGetQuery(con, "SELECT * FROM Prog
                         WHERE ID_number = '842517'")
```




***

###C. Doing questions 3, 4, 5

####Question3: INNER JOIN and other JOINs
(a.) Inner join
```{r, message = F}
inner_join <- dbGetQuery(con, "SELECT * 
                   FROM Diag
                    INNER JOIN Prog
                    USING (ID_number);") 
```

```{r}
head(inner_join)
```

(b.) Left join

```{r, message = F}
left_join <- dbGetQuery(con, "SELECT * FROM Diag
                        LEFT JOIN Prog
                        USING (ID_number);")
```
```{r}
head(left_join)
```

(c.) Left excluding join
```{r, message = F}
left_excluding <- dbGetQuery(con, "SELECT * FROM Diag
                             LEFT JOIN Prog
                             USING (ID_number);
                             WHERE Prog.ID_number IS NULL")
```

```{r}
head(left_excluding)
```





***

####Question4: Use GROUP BY and Aggregation
```{r, message = F}
#Group By the Prognostic data with "outcome"
group_by_prognostic <- dbGetQuery(con, "SELECT outcome, COUNT(ID_number), AVG(time)
                       FROM Prog
                       GROUP BY outcome")
group_by_prognostic
```
```{r, message = F}
#Group By the Diagnostic data with "Diag" (This colname means the final diagnostic result)
group_by_diagnostic <- dbGetQuery(con, "SELECT Diag, COUNT(ID_number),
                                  AVG(mean_radius)
                                  FROM Diag
                                  GROUP BY Diag")
```





***
####Question5: Order by
```{r, message = F}
#Order the prognostic data
order_by_prognostic <- dbGetQuery(con, "SELECT outcome, COUNT(ID_number),
                                  AVG(time)
                                  FROM Prog
                                  GROUP BY outcome
                                  ORDER BY AVG(time)")
```

```{r, message = F}
#Order the diagnostic data
order_by_diagnostic <- dbGetQuery(con, "SELECT Diag, COUNT(ID_number),
                                  AVG(mean_radius)
                                  FROM Diag
                                  GROUP BY Diag
                                  ORDER BY AVG(mean_radius)")
```




***
###D. Errors I encountered 

####1. When I Use "RMySQL" package - Cannot connect to database
```{r, message = F}
library(RMySQL)
```

Q: Cannot connect db - Cannot connect to MySQL server on "localhost" and "My IP address"
```{r}
#I cannot run the following codes because it will show error message
#connect <- dbConnect(MySQL(), user = "Eve", password = "j33890",
#                     dbname = "database.sqlite",
#                     host = "localhost")

#connect <- dbConnect(MySQL(), user = "Eve", password = "j33890",
#                     dbname = "database.sqlite",
#                     host = "192.168.2.114")

```
The error messages look like this:
Error in .local(drv, ...) : 
  Failed to connect to database: Error: Can't connect to MySQL server on 'localhost' (0)
  
  
  
***
####2. When I Use "RSQLite" package - cannot set primary keys
```{r}
###dbGetQuery(con, "SHOW INDEX FROM Diag")
```
